Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-09 bbbq_article.tex
Add normalized perc binders that is TMH to manuscript, fix https://github.com/richelbilderbeek/bbbq_article/issues/90

@@

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc1_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}
